Using R to help plan the <br> future of transport

### 2018-11-19 ms-meetup-nov18.Rmd
:wrench:Rmd

>>>>

- The fastest and easiest method in any language for extracting OSM data
- Only software that allows OSM data to be extracted in 3 simple lines:

```{r, eval = FALSE}
ms <- opq ("münster de") %>%
    add_osm_feature (key = "highway") %>%
    osmdata_sf (quiet = FALSE)
```

- Extremely flexible; can extract any form of OSM data.
